### 2019-03-07 soc.tex
make captions non-bold
Although bold captions arguably look a lot better than normal captions, both of the formatting documents have them formatted this way.

% CAPTIONS %
%-========-%
\usepackage[font=footnotesize,        % 10pt captions
            labelfont=bf,             % bold captions
            justification=centering,  % center the captions
            figurename=Obr.,          % picture captions are "Obr."
            tablename=Tab.,           % table captions are "Tab."
            belowskip=-12pt]{caption} % reduce skip below figures

>>>>

% CAPTIONS %
%-========-%
\usepackage[font=footnotesize,        % 10pt captions
            justification=centering,  % center the captions
            figurename=Obr.,          % picture captions are "Obr."
            tablename=Tab.,           % table captions are "Tab."
            belowskip=-12pt]{caption} % reduce skip below figures
